\chapter*{Introduction}

This document serves as a theory guide for the multiphase framework of TRUST/TrioCFD. In brief, using the HPC platform TRUST, TrioCFD allows to perform two-phase flow RANS computation in the modelling paradigm where phases are considered continuous. It allows the computation of the flow of an arbitrary number of phases. Continuous equations for mass, momentum and energy are solved for each phase. For the classical case of two phases, one continuous and the other discrete, this system gives the classical six-equations-single-pressure Euler-Euler model. Using a special operator which allows to handle vanishing phases, this system can easily be simplified to handle any equilibrium. As a result, the same framework allows to simulate, for instance, a homogeneous equilibrium model. Currently, three approaches are available and documented: the six-equation-single-pressure model, the drift-velocity model and the HEM model. It consists on a set of source terms to the previously mentioned conservation equations. Single-phase RANS modelling is obviously available. Turbulence can currently be taken into account for the continuous phase only. The document describes the available time and spatial schemes. Details are given on the boundary conditions. Being a shared computing platform for several applications, a list of validation test cases is provided for each module based on the multiphase framework.

Technicalities are given on the links between mathematical formulation of algorithms and their implementation. To assist development, some details are provided about the coding standard. The documentation tries to follow the implementation in the code to described what is actually performed in the code. The origin of physical models is given in bibliography when available, or details about the intention of the developer are provided for in-house models.

In its current version, details are given about the shape of the input file. Some aspects about the \texttt{C++ architecture} are also provided to guide the user and developer in the file location between TRUST and TrioCFD.

Any remark or recommendation of improvment is welcome and can be emailed at \href{mailto:trust@cea.fr}{trust@cea.fr}.
